Chord: A Static and Dynamic Program Analysis Framework for Java

### 2011-03-04 main/doc/building_scope.tex
documentation

\section{Computing Program Scope}
\label{sec:building-scope}

@@

\subsection{Reusing Program Scope}

@@

\subsection{Scope Construction Algorithms}

@@

\item
The {\tt rta} value instructs Chord to compute program scope
statically using Rapid Type Analysis (RTA).

RTA is an iterative fixed-point algorithm.  It maintains a set of
reachable methods $M$.  The initial iteration starts by assuming that
only the main method in the main class is reachable (Chord also
handles class initializer methods but we ignore them here for brevity;
we also ignore the set of reachable classes maintained besides the set
of reachable methods).  All object allocation sites $H$ contained in
methods in $M$ are deemed reachable (i.e., control-flow within method
bodies is ignored).  Whenever a dynamically-dispatching method call
site (i.e., an invokevirtual or invokeinterface site) with receiver of
static type $t$ is encountered in a method in $M$, only subtypes of
$t$ whose objects are allocated at some site in $H$ are considered to
determine the possible target methods, and each such target method is
added to $M$.  The process terminates when no more methods can be
added.

%RTA is a relatively inexpensive and precise algorithm in practice.  Its key shortcoming is that it makes
%no attempt to resolve reflection, which is rampant in real-world Java programs, and can therefore be
%unsound (i.e., underestimate the set of reachable classes and methods).
%The next option attempts to overcome this problem.
%
%\item
%The \code{rta_reflect} value instructs Chord to compute program scope statically using Rapid Type Analysis
%and, moreover, to resolve a common reflection pattern:
%
%\begin{quote}
%\begin{verbatim}
%String s = ...;
%Class c = Class.forName(s);
%Object o = c.newInstance();
%T t = (T) o;
%\end{verbatim}
%\end{quote}
%
%This analysis is identical to RTA except that it additionally inspects every cast statement in the program,
%such as the last statement in the above snippet,
%and queries the class hierarchy to find all concrete classes that subclass \code{T} (if \code{T} is a class)
%or that implement \code{T} (if \code{T} is an interface).
%Chord allows users to control which classes are included in the class hierarchy (see below).
%
\item
The {\tt cha} value instructs Chord to compute program scope
statically using Class Hierarchy Analysis (CHA).

The key difference between CHA and RTA is that for invokevirtual and
invokeinterface sites with receiver of static type $t$, CHA considers
{\it all} subtypes of $t$ in the class hierarchy to determine the
possible target methods, whereas RTA restricts them to types of
objects allocated in methods deemed reachable so far.  As a result,
CHA is highly imprecise in practice, and also expensive since it
grossly overestimates the set of reachable classes and methods.
Nevertheless, Chord allows users to control which classes are
included in the class hierarchy (see below) and thereby control the
precision and cost of CHA.

@@

\subsection{Class Hierarchy Construction}

@@

\subsection{Scope Exclusion}

%TODO: describe chord.scope.exclude?

>>>>

\section{Computing program scope}
\label{sec:building-scope}

@@

\subsection{Scope reuse}

@@

\subsection{Scope construction algorithms}

@@

\item
The {\tt rta} value instructs Chord to compute program scope
statically using Rapid Type Analysis (RTA).
RTA is an iterative fixed-point algorithm.  It maintains a set of
reachable methods $M$.  The initial iteration starts by assuming that
only the main method in the main class is reachable (Chord also
handles class initializer methods but we ignore them here for brevity;
we also ignore the set of reachable classes maintained besides the set
of reachable methods).  All object allocation sites $H$ contained in
methods in $M$ are deemed reachable (i.e., control-flow within method
bodies is ignored).  Whenever a dynamically-dispatching method call
site (i.e., an invokevirtual or invokeinterface site) with receiver of
static type $t$ is encountered in a method in $M$, only subtypes of
$t$ whose objects are allocated at some site in $H$ are considered to
determine the possible target methods, and each such target method is
added to $M$.  The process terminates when no more methods can be
added.

%RTA is a relatively inexpensive and precise algorithm in practice.
%Its key shortcoming is that it makes no attempt to resolve
%reflection, which is rampant in real-world Java programs, and can
%therefore be unsound (i.e., underestimate the set of reachable
%classes and methods).  The next option attempts to overcome this
%problem.  \item The \code{rta_reflect} value instructs Chord to
%compute program scope statically using Rapid Type Analysis and,
%moreover, to resolve a common reflection
%pattern: \begin{quote} \begin{verbatim} String s = ...; Class c =
%Class.forName(s); Object o = c.newInstance(); T t = (T)
%o; \end{verbatim} \end{quote} This analysis is identical to RTA
%except that it additionally inspects every cast statement in the
%program, such as the last statement in the above snippet, and queries
%the class hierarchy to find all concrete classes that subclass
%\code{T} (if \code{T} is a class) or that implement \code{T} (if
%\code{T} is an interface).  Chord allows users to control which
%classes are included in the class hierarchy (see Section
%\ref{sec:cha}).
\item
The {\tt cha} value instructs Chord to compute program scope
statically using Class Hierarchy Analysis (CHA).
The key difference between CHA and RTA is that for invokevirtual and
invokeinterface sites with receiver of static type $t$, CHA considers
{\it all} subtypes of $t$ in the class hierarchy to determine the
possible target methods, whereas RTA restricts them to types of
objects allocated in methods deemed reachable so far.  As a result,
CHA is highly imprecise in practice, and also expensive since it
grossly overestimates the set of reachable classes and methods.
Nevertheless, Chord allows users to control which classes are
included in the class hierarchy (see \ref{sec:cha}) and thereby control the
precision and cost of CHA.

@@

\subsection{Class hierarchy construction}
\label{sec:cha}

@@

\subsection{Scope exclusion}

For tractability, Chord can be instructed to treat the bodies of certain
methods as no-ops.  Chord provides three properties for this purpose.
The value of each of these properties is a comma-separated list of prefixes
of names of classes all of whose declared methods must be treated as no-ops:

\begin{itemize}
\item
Property \code{chord.std.scope.exclude} conventionally specifies
classes to be excluded from the scope of {\it all} programs to be
analyzed, e.g., classes in the JDK standard library.  Its default
value is \code{[chord.main.class.path]}, i.e., the classes comprising
Chord itself.
\item
Property \code{chord.ext.scope.exclude} conventionally specifies
classes to be excluded from the scope of specific programs to be
analyzed.  Its default value is the empty list.
\item
Property \code{chord.scope.exclude} specifies the final list of
classes to be excluded from scope.  Its default value is simply the
concatenation of the values of properties
\code{chord.std.scope.exclude} and \code{chord.ext.scope.exclude}.
\end{itemize}

### 2011-03-04 main/doc/download_and_installation.tex
documentation

\section{Download and Installation}
\label{sec:download-and-installation}

@@

\begin{itemize}
\item
JDK 5 or higher, e.g. from
\xlink{IBM}{http://www.ibm.com/developerworks/java/jdk/} or
\xlink{Sun}{http://java.sun.com/javase/downloads/index.jsp}
\item
\xlink{Apache Ant}{http://ant.apache.org/}, a Java-based build tool
\item
a C++ compiler, e.g. \xlink{GCC}{http://gcc.gnu.org/}
\item
a Make utility, e.g. \xlink{GNU Make}{http://www.gnu.org/software/make/}
\item
\xlink{Cygwin}{http://www.cygwin.com/}, if it is a Windows machine
\end{itemize}

Download the latest Chord source code from the SVN repository:

@@

@@

\noindent To compile Chord, run the following command in the same
directory:

\begin{verbatim}
    prompt> ant compile
\end{verbatim}

\noindent This will compile the following:
\begin{itemize}
\item
the Java source code of Chord from \code{main/src/} to Java bytecode
in \code{main/classes/}.
\item
the C source code of BDD library
\xlink{BuDDy}{http://buddy.sourceforge.net/} from
\code{main/bdd/} to a shared library in \code{main/lib/}
(\code{libbuddy.so} on Linux, \code{buddy.dll} on Windows, and
\code{libbuddy.dylib} on MacOS); this library is needed for executing
program analyses written in Datalog using
\xlink{bddbddb}{http://bddbddb.sourceforge.net/} (a
BDD-based Datalog solver).
\item
the C++ source code of the Chord instrumentation agent from
\code{main/agent/} to a shared library in \code{main/lib/}
(\code{libchord_instr_agent.so} on all architectures); this agent is
needed for computing program scope dynamically and for executing
dynamic program analyses.
\end{itemize}

>>>>

\section{Download and installation}
\label{sec:download-and-installation}

@@

\begin{itemize}
\item
A JVM with JDK 5 or higher, e.g.
\xlink{IBM J9}{http://www.ibm.com/developerworks/java/jdk/} or
\xlink{Oracle HotSpot}{http://www.oracle.com/technetwork/java/javase/downloads/index.html}
\item
\xlink{Apache Ant}{http://ant.apache.org/}, a Java-based build tool
\end{itemize}

{\bf Note:} If you intend to use Chord for dynamic analysis, then
IBM J9 is highly recommended, as it allows you to instrument
the entire JDK; using any other JVM will likely require excluding
large parts of the JDK from being instrumented.

Obtain the latest stable release of Chord from \url{http://jchord.googlecode.com/checkout/}
or the latest development snapshot from the SVN repository:

@@

\begin{verbatim}
    prompt> ant help
\end{verbatim}

\noindent To compile Chord, simply run the following command in the same
directory:

@@

\noindent This will compile
the Java source code of Chord from \code{main/src/} to Java bytecode
in \code{main/classes/}.
Additionally:
\begin{itemize}
\item
If system property \code{chord.use.buddy} is set to true (default is false),
then the C source code of BDD library
\xlink{BuDDy}{http://buddy.sourceforge.net/} from
\code{main/bdd/} will be compiled to a shared library in \code{main/lib/}
(\code{libbuddy.so} on Linux, \code{buddy.dll} on Windows, and
\code{libbuddy.dylib} on MacOS); this library is used for executing
program analyses written in Datalog using
\xlink{bddbddb}{http://bddbddb.sourceforge.net/} (a
BDD-based Datalog solver).
\item
If system property \code{chord.use.jvmti} is set to true (default is false),
then the C++ source code of the Chord instrumentation agent from
\code{main/agent/} will be compiled to a shared library in \code{main/lib/}
(\code{libchord_instr_agent.so} on all architectures); this agent is
used for computing program scope dynamically and for executing
dynamic program analyses.
\end{itemize}
The above system properties can be set either in file \code{main/chord.properties}
(recommended) or on the command line as follows:

\begin{verbatim}
    prompt> ant -Dchord.use.buddy=true -Dchord.use.jvmti=true
\end{verbatim}

### 2011-03-04 main/doc/whatis_chord.tex
documentation

Chord is a program analysis platform for Java designed with the
primary goal of helping advance the state-of-the-art in the field by
enabling researchers to productively design, implement, and evaluate a
broad variety of program analyses. To this end, Chord has the
following key characteristics:

\begin{itemize}
\item
Stand-alone: it provides various off-the-shelf analyses (e.g., various
call-graph analyses; points-to analyses; thread-escape analysis;
static slicing; static and dynamic concurrency analyses for finding
races, deadlocks, and atomicity violations; etc.)
\item
Extensible: it allows users to build their own analyses atop the
provided analyses.
\item
Compositional: it allows users to write each analysis independently
yet allow it to interact in complex ways with other analyses by
specifying lightweight data- and control-dependencies.
\item
Efficient: It executes analyses in a demand-driven fashion, caches
results computed by each analysis for reuse by other analyses without
re-computation, and can execute analyses without dependencies between
them in parallel.
\item
Deterministic: It guarantees that the result is the same regardless of
the order in which different analyses are executed; moreover, results
can be shared across different runs.
\item
Flexible: It allows a broad range of analyses to be expressed,
including both static and dynamic analyses, analyses written
imperatively in Java or declaratively in Datalog, summary-based as
well as cloning-based inter-procedural context-sensitive analyses,
iterative refinement-based analyses, client-driven analyses, and
combined static/dynamic analyses.
\end{itemize}

\noindent Chord is intended to work on a variety of platforms,
including Linux, Windows/Cygwin, and MacOS.  It has been tested most
extensively on Linux.  It is open source software distributed under
the \xlink{New BSD License}{http://www.opensource.org/licenses/bsd-license.php}.
Improvements by users are welcome and encouraged.  The project website
is \url{http://berkeley.intel-research.net/chord/} and the software
website is \url{http://code.google.com/p/jchord/}.

>>>>

Chord is a program analysis platform that enables 
productively design, implement, evaluate, and combine a
broad variety of program analyses for Java bytecode. It has the
following key features:

\begin{itemize}
\item
{\bf Stand-alone:} It provides various off-the-shelf analyses (e.g., various
call-graph analyses; points-to analyses; thread-escape analysis;
static slicing; static and dynamic concurrency analyses for finding
races, deadlocks, and atomicity violations; etc.)

\item
{\bf Flexible:} It allows users to express a broad range of analyses,
including both static and dynamic analyses, analyses written
imperatively in Java or declaratively in Datalog, summary-based as
well as cloning-based inter-procedural context-sensitive analyses,
iterative refinement-based analyses, client-driven analyses, and
combined static/dynamic analyses.

\item
{\bf Efficient:} It executes analyses in a demand-driven fashion, caches
results computed by each analysis for reuse by other analyses without
re-computation, and can execute analyses without dependencies between
them in parallel.

\item
{\bf Deterministic:} It guarantees that the result is the same regardless of
the order in which different analyses are executed; moreover, results
can be shared across different runs.
\end{itemize}

\noindent Chord is intended to work on a variety of platforms,
including Linux, Windows/Cygwin, and MacOS.  It has been tested most
extensively on Linux.  It is open source software distributed under
the \xlink{New BSD License}{http://www.opensource.org/licenses/bsd-license.php}.
Improvements by users are welcome and encouraged.  The project website
is \url{http://chord.stanford.edu/} and the software development website is
\url{http://jchord.googlecode.com/}.
